Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-01 latex/robdml.tex
tex

\textbf{Adversarial Attack.}

\textbf{Adversarial Defense.}

\textbf{Deep Metric Learning.}
\cite{advrank,advorder,robrank}

>>>>

\textbf{Adversarial Attack.}
%
Szegedy \etal~\cite{l-bfgs} find misclassification of DNN can be triggered by
an imperceptible adversarial perturbation to the input image.
%
Ian \etal~\cite{fgsm} speculate the reason is that DNN being locally linear
with respect to the adversarial perturbation.
%
A series of following works attempt to more efficiently compromise the DNNs,
such as BIM~\cite{i-fgsm}, C\&W~\cite{cw}, PGD~\cite{madry}, and
APGD~\cite{apgd}.
%
These attacks are based on the first-order gradient of the classification loss
with respect to the input image, and hence rely on the white-box assumption
that the model architecture and parameters are accessible to the attacker,
which is impractical for real-world attacks.
%
Subsequently, black-box attack methods are developed into two types:
transferrability-based attacks and query-based attacks.
%
Transferrability-based attacks relies on the observation that image-agnostic
(will take effect when applied to any image) and model-agnostic (will take
effect when applied to any model) adversarial perturbation are possible.
%
Query-based attacks only need the logit score output or the label output from a
classifier, based on which the gradient could be estimated from the response to
repetitive queries in order to figure out the adversarial perturbation.

\textbf{Adversarial Defense.}
%
To battle against the attacks, some early defense
methods create a gradient masking effect, namely making it hard for the attacker
to find a good gradient, but it gives a false sense of security~\cite{obfuscated}.
%
Defensive distillation~[] can be compromised by C\&W~\cite{cw}.
%
Ensemble of weak defenses is insufficient~[].
%
Defense can also be implemented as preprocessing~[] or reconstructing~[] the input
image, or a randomized process inside the network~[].
%
However, it is noted that various defense methods are still susceptible to
adaptive attack~\cite{adaptive}.
%
Among the proposed defense methods, adversarial training has been empirically
found effective~[][], and it consistently retains adversarial robustness
for the model.

\textbf{Deep Metric Learning.}
%
A wide range of application problem such as image retrieval~\cite{imagesim2},
cross-modal retrieval~\cite{ladderloss}, and face recognition~\cite{facenet}
can be formularized as a deep metric learning problem.
%
Deep metric learning has been found vulnerable to adversarial attacks as
well~\cite{advrank,advorder}, which will result in undesired
implications on safety, security, or fairness of a deep metric learning
application.
%
In contrast, the defense methods for enhancing the adversarial robustness of deep
metric learning are less explored.
%
Mo \etal~\cite{advrank} present an adversarial training method with adversarial
examples maximizing the embedding move distance off its original location.
%
Anti-Collapse Triplet defense~\cite{robrank} forces the model
to separate collapsed positive and negative samples in order to learn
robust features.
%
However, the existing defense methods refrain from adopting Madry's min-max
adversarial training paradigm due to the model being too easy to collapse
with excessively hard adversarial samples.
